Constraints on the mass and occupation fraction of dark matter halos hosting Lyman-alpha emitters at $z\sim 3$

### 2013-06-27 paper/ms.tex
minor update

The preference for narrow $\Delta M$ ranges to hosting LAEs together
with the total absence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun \  shows that our models support theoretical insights
where the most massive systems are not bright \ly sources
\citep{ForeroRomero2012}.

>>>>

The preference for narrow $\Delta M$ ranges to hosting LAEs together
with the minor presence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun \  shows that our models support theoretical insights
where the most massive systems are not bright \ly sources
\citep{ForeroRomero2012}.
